Performance Evaluation of Big Data Processing Strategies for Neuroimaging

### 2018-12-03 paper.tex
some text on nipype

>>>>

Nipype is a popular Python neuroimaging processing engine. It aims at being a 
solution for easily creating reproducible neuroimaging workflows. Although Nipype
does not employ any Big Data processing strategies, it provides access to numerous
plugins to schedulers found in most clusters readily available to researchers, 
such as SGE, PBS, SLURM and HTCondor. It also includes its own scheduler, MultiProc,
for parallel processing on single nodes. Nipype also includes many built-in 
interfaces to commonly used neuroimaging tools to be incorporated within the 
workflows. Nipype's ability to easily parallelize workflows in researcher-available 
cluster setups, capture detailed provenance information necessary for reproducibility
and allow users to easily integrate existing neuroimaging tools, make it preferable
to existing Big Data solutions, which would necessitate modification to achieve this.

Jobs, or Interfaces, in Nipype, are encapsulated by a Node. A Node dictates that
the job will execute on a single input. However, there are exists the MapNode, 
a child variant of the Node, which can execute on multiple inputs. All tasks in
Nipype execute in their own uniquely named subdirectory which enables the provenance 
tracking of inputs and outputs. This also enables checkpointing of the workflow.
In the case of Node failure or application modification, only the nodes who have
been modified (verified by hash) are re-executed.

In order for Nipype to operate as intended, a filesystem shared by all the nodes 
is required. However, it is still possible to save to a non-shared local filesystem, 
but it may come at the expense of fault-tolerance. Moreover, the user will need to
ensure that the files are appropriately directed to the nodes that require them as
there is no guarantee of data locality in Nipype.
